---
title: "Cox models peptidomics Godarts"
author: "Gerard"
date: "Janurary 03, 2019"
output: md_document
---

```{r setup, include=FALSE, eval=F}
knitr::opts_knit$set(root.dir = "D:/001_Projects/001_RHAPSODY/")
```

## Load libraries and Utils scripts
```{r prep,results='hide',message=FALSE,warning=FALSE, eval=F}
library(datashieldclient)
library(dsCDISCclient)
library(survminer)
library(survival)

#Load utils
source("./Utils/Utils_GB.R")
source("./Utils/Utils_CoxModels.R")
```

## Login
```{r,message=FALSE,warning=FALSE,results='hide', eval=F}
loginpath <- "./logindata_template.txt"
cohort <- "godarts"
datasource <- "opal"
logIn(datasource, loginpath, cohort)
```

## Prepare Data
```{r preparedata,results='hide', eval=F}
#Select required attributes 
myAttributes <- c("SOMALOGIC","MEDICATION","BMI","AGE","SEX","HDL","HBA1C","CPEPTIDE","TIMETOINSULIN",
	"TIMEINSULINSTATUS","DIABDUR","TimeToSpin")
myTransform <-c(3,0,0,0,0,0,0,0,0,0,0,0)
prepareData(assign="ModelData",opal=opal,attributes=myAttributes,transformVector=myTransform)

```

## Prepare Formulas
```{r prepareFormulas, eval=F}
#MODEL 1 
PeptidesFormula1 <- "survival::Surv(TIMEINSULIN, LBTESTCD.TIMEINSULINSTATUS) ~ %s +
                             survival::strata(cut(LBTESTCD.HBA1C ,breaks=c(0,53,75,140))) + age + sex + VSTESTCD.BMI + LBTESTCD.TimeToSpin "
#MODEL 2
PeptidesFormula2 <- "survival::Surv(TIMEINSULIN, LBTESTCD.TIMEINSULINSTATUS) ~ %s +
                             survival::strata(cut(LBTESTCD.HBA1C ,breaks=c(0,53,75,140))) + age + sex + VSTESTCD.BMI + LBTESTCD.HDL + LBTESTCD.CPEPTIDE + LBTESTCD.TimeToSpin"
#MODEL 3
PeptidesFormula3 <- ("survival::Surv(TIMEINSULIN, LBTESTCD.TIMEINSULINSTATUS) ~ %s +
                             survival::strata(cut(LBTESTCD.HBA1C ,breaks=c(0,53,75,140))) + age + sex + VSTESTCD.BMI + LBTESTCD.HDL + LBTESTCD.CPEPTIDE + DIABETESDURATION + glucoselowering + LBTESTCD.TimeToSpin")

```

## Prepare arguments for function call
```{r PrepareArguments, eval=F}
load("./Data/Conversion_Peptides.RData")
targets <- conversion;rm(conversion)
peptides <- ds.colnames('ModelData')$godarts
peptides <- peptides[which(peptides == "LBTESTCD.SL000001"):which(peptides=="LBTESTCD.SL021043")]
```

## Calculate Cox models for model 1
HbA1c, Age, Sex, BMI, TimeToSpin
```{r PeptideModel1,results='hide', eval=F}
PeptidesModel1 <- CalculateCoxModel(vars = peptides[1:600],
                                    formula = PeptidesFormula1,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel1.2 <- CalculateCoxModel(vars = peptides[601:1195],
                                    formula = PeptidesFormula1,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel1GODARTS <- rbind(PeptidesModel1,PeptidesModel1.2)
PeptidesModel1GODARTS$fdr <- p.adjust(PeptidesModel1GODARTS$p.val,method="fdr")
```

```{r PeptideModel1Out, eval=F}
save(PeptidesModel1GODARTS,file="SomalogicgodartsCoxModel1.RData")
knitr::kable(head(PeptidesModel1GODARTS[order(PeptidesModel1GODARTS$fdr,decreasing = F),],10))
```

## Calculate Cox models for model 2
HbA1c, Age, Sex, BMI, HDL , CPeptide, Time to Spin
```{r PeptideModel2,results='hide', eval=F}
PeptidesModel2 <- CalculateCoxModel(vars = peptides[1:600],
                                    formula = PeptidesFormula2,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel2.2 <- CalculateCoxModel(vars = peptides[601:1195],
                                    formula = PeptidesFormula2,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel2GODARTS <- rbind(PeptidesModel2,PeptidesModel2.2)
PeptidesModel2GODARTS$fdr <- p.adjust(PeptidesModel2GODARTS$p.val,method="fdr")

```


```{r PeptideModel2Out, eval=F}
save(PeptidesModel2GODARTS,file="SomalogicgodartsCoxModel2.RData")
knitr::kable(head(PeptidesModel2GODARTS[order(PeptidesModel2GODARTS$fdr,decreasing = F),],10))
```

## Calculate Cox models for model 3
HbA1c, Age, Sex, BMI, HDL , CPeptide, Diabetes Duration, Glucose Lowering Drugs, Time to Spin
```{r PeptideModel3,results='hide', eval=F}
PeptidesModel3 <- CalculateCoxModel(vars = peptides[1:600],
                                    formula = PeptidesFormula3,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel3.2 <- CalculateCoxModel(vars = peptides[601:1195],
                                    formula = PeptidesFormula3,
                                    targets = targets,cohort = "godarts",
                                    omicType = "SOMALOGIC",
                                    data = "ModelData")

PeptidesModel3GODARTS <- rbind(PeptidesModel3,PeptidesModel3.2)
PeptidesModel3GODARTS$fdr <- p.adjust(PeptidesModel3GODARTS$p.val,method="fdr")
```

```{r PeptideModel3Out, eval=F}
save(PeptidesModel3GODARTS,file="SomalogicgodartsCoxModel3.RData")
knitr::kable(head(PeptidesModel3GODARTS[order(PeptidesModel3GODARTS$fdr,decreasing = F),],10))
```

## Logout
```{r logout, eval=F}
logOut(datasource)
```